---
title: "Investigate a difference in pattern of Influenza Outbreak between different regions"
author: Choi Dongon
---

# Introduction

Contact networks between individuals play a significant role in influenza transmission. However, hitherto, many strategies to control influenza transmission have been designed without a consideration for a difference in contact networks by different regions. The pattern of contact networks in each region is changed by age distributions, economic activities, social status and et al, and thus yielding a different influenza outcome by regions. To investigate these issues, the main objectives of this project are two-fold: 1) to simulate influenza outbreaks at different contact network patterns by regions, and 2) to assess a difference in the outcomes of influenza pandemics between regions. 

# Materials and methods

To simulate influenza outbreaks, first we need US census data for age distribution, economic activities on Buffalo city, NY.
```{r}
## load demographic data for Buffalo city
read.csv('data/demographic.csv')
```


You can do bullets like this:

* The first most important thing
* The second most important thing
* The third most important thing

You can do numbers like this:

1. The first most important thing
2. The second most important thing
3. The third most important thing

Load any required packages in a code chunk (you may need to install some packages):

```{r, message=F, warning=F}
library(ggplot2)
library(maps)
library(spocc)
```

# Results

Show tables, plots, etc. and describe them.
```{r}
summary(d)
```


# Conclusions

What have you learned?  Are there any broader implications?

# References