---
title: "Visualize Noise pollution in New York Ci111ty"
subtitle: "Using NYC311 Service Requests Dataset"
author: Choi Dongon
---

# Introduction

Contact networks between individuals play a significant role in influenza transmission. However, hitherto, many strategies to control influenza transmission have been designed without a consideration for a difference in contact networks by different regions. The pattern of contact networks in each region is changed by age distributions, economic activities, social status and et al, and thus yielding a different influenza outcome by regions. To investigate these issues, the main objectives of this project are two-fold: 1) to simulate influenza outbreaks at different contact network patterns by regions, and 2) to assess a difference in the outcomes of influenza pandemics between regions. 

Recently, noise pollution is the one of problems in urbanized area, especially in metropolitan area such as New York City, Cichago, and Los Angelos. Noise pollution significantly interventm, ultimatlely can cause 떨어뜨리다 their healthy life.

In this project, I will investigate noise pollution in NYC by visualizing and analying spatio-temproal perspective.

# Materials and methods

Load required packages
```{r, message=F, warning=F}
## Load any required packages in a code chunk; you may need to install some packages below using a code 'install.packages('PACKAGE NAME')
library(dplyr)
library(tidyr)
library(ggmap)
library(ggplot2)
library(openair)
library(zipcode)
```

Import dataset & Data cleaning
```{r}
## Load NYC 311 noise complaints data
#noisedata<-read.csv('data/311.csv')

## Filter NYC 311 dataRemove missing data
#noise <- filter(noise, !is.na(Latitude) | !is.na(Longitude))
```





# Results

# Conclusions

# References